Library Learning in Neurally-Guided Bayesian Program Induction

### 2018-10-26 nips_2018.tex
tweaks to discussion

 We have presented an algorithm that, starting from relatively little,
 learned to solve nontrivial program synthesis problems in three
 different domains.  However, our system was also given (and also,
 critically \emph{needs}) a corpus of training tasks to solve for each
 domain.  Is constructing (or curating) corpra of tasks any easier or
 better than hand-engineering DSLs?  In the immediate future, we
 expect hand-engineering of DSLs to largely continue, especially in
 domains where humans have strong intuitions about the underlying
 system of domain specific concepts, like text editing. However, if
 program induction is to become a standard part of the AI toolkit,
 then, in the long-term, we need to build agents that autonomously
 acquire the domain specific knowledge needed to navigate a new
 domain.  So, through the lens of program synthesis, EC$^2$ carries
 the limitation that it requires a high-quality corpus of training
 tasks; but, for the program-induction approach to AI, this limitation
 is natural.

>>>>

 We have presented an algorithm that, starting from relatively little,
 learned to solve nontrivial program synthesis problems in three
 different domains.  However, our system was also given (and also,
 critically \emph{needs}) a corpus of training tasks to solve for each
 domain.  Is constructing (or curating) corpra of tasks any easier or
 better than hand-engineering DSLs?  In the immediate future, we
 expect some degree of hand-engineering of DSLs to continue, especially
 in domains where humans have strong intuitions about the underlying
 system of domain specific concepts, like text editing. However, if
 program induction is to become a standard part of the AI toolkit,
 then, in the long-term, we need to build agents that autonomously
 acquire the domain specific knowledge needed to navigate a new
 domain.  So, through the lens of program synthesis, EC$^2$ carries
 the limitation that it requires a high-quality corpus of training
 tasks; but, for the program-induction approach to AI, this limitation
 is natural.
